Attack-Tolerance in Structured Networks via Multipath Routing

### 2016-02-24 ec-2016/source/paper.tex
Frantic last minute changes.

TODO:\\
Fix bibtex encoding\\
Move secrecy section\\
Update intro to make significance more clear\\
Clarify identifying fault\\

@@

We consider a setting in which a source node in a network attempts to route information
to a target node by forwarding it through the links of the network. We 
assume that some nodes in the network may be compromised by an attacker 
and will forward the wrong information to their neighbors or
block the information altogether.
In order to evaluate network-based techniques for mitigating such attacks,
we develop a decentralized {\em partial trust} model,
similar to a web of trust
\cite{zimmermann_official_1995,ferguson_practical_2003},
but making weaker assumptions of trust transitivity.

Given this framework, we develop and evaluate a \emph{multipath routing} technique to reduce 
the likelihood that compromised nodes are undetected during the information 
routing process by allowing multiple copies of a message to be sent through independent paths,
which can be used for error-detection and error-correction by the receiver.

@@

\item[Secrecy]
In some, but not all cases, it is desirable that the infrastructure provides secrecy and allow a source and a target to exchange private information while still relying on intermediary nodes. Our proposed multipath routing technique can be adapted to provide secrecy but we do not focus on this aspect in this paper.

@@

When the assumptions of the partial trust model hold, a network can achieve
robust fault tolerance by utilizing the redundancy of multiple paths
between the sender and receiver.
Furthermore, this fault tolerance can remain robust even when faults are
adversarially chosen by an attacker who has access to more resources
than the sender and receiver.
On a structured network, multipath fault tolerance reveals not just when
an error has occured, but also which routes are faulty and potentially
compromised.

@@

Secrecy

Creation of the network.
Improves on web of trust.
Gives framework for determining where to build trust.

Applications
Distributed apps: storage, email, cryptocurrency, secure multiparty computation.
Wireless Sensor Networks

@@

% Acknowledgments
\begin{acks}
The authors would like to thank TODO
\end{acks}

>>>>

%TODO:\\
%Fix bibtex encoding\\
%Move secrecy section\\
%Update intro to make significance more clear\\
%Clarify identifying fault\\

@@

We consider a setting in which a source node in a network attempts to route information
to a target node by forwarding it through the links of the network. We 
assume that some nodes in the network may be compromised by an attacker 
and will forward the wrong information to their neighbors or
block the information altogether.
In order to evaluate network-based techniques for mitigating such attacks,
we develop a decentralized {\em partial trust} model,
similar to a web of trust
\cite{zimmermann_official_1995,ferguson_practical_2003},
but making weaker assumptions of trust transitivity.
While privacy and secrecy are often concerns in secure communication,
it is not the focus of this paper.
Existing techniques for privacy and secrecy are relatively mature compared
to those for tolerating blocked or corrupted messages.
In fact, an attacker might use message disruption as a fallback when
surveillance isn't feasible.
However, we would like to stress that the technqiues presented in this paper
are entirely compatible with, and in some cases could enhance, existing
privacy and secrecy techniques.

Given the above framework, we develop and evaluate a \emph{multipath routing} technique to reduce 
the likelihood that compromised nodes are undetected during the information 
routing process by allowing multiple copies of a message to be sent through independent paths,
which can be used for error-detection and error-correction by the receiver.

@@

@@

When the assumptions of the partial trust model hold, a network can achieve
robust fault tolerance by utilizing the redundancy of multiple paths
between the sender and receiver.
Furthermore, this fault tolerance can remain robust even when faults are
adversarially chosen by an attacker who has access to more resources
than the sender and receiver.
On a structured network, multipath fault tolerance reveals not just when
an error has occured, but also provides information about which paths provide
conflicting information,
which could be used to help locate compromised nodes.

@@

While decentralized architectures have recieved much attention,
methods for classifying, and evaluating decentralization
are in their infancy.
The trust model and multipath fault tolerance technique proposed in this
paper provide a practical fault tolerance architecture for applications when
network structure can be imposed,
as well as a more general method for evaluating the role of network structure
on fault tolerance.

Fault-tolerant network infrastructures have many direct applications.
Areas such as cryptocurrency, secure multiparty computation, and wireless
sensor networks have immediate need for scalable, fault-tolerant
infrastructures.
Many Internet services---email, social networks, cloud storage---are still
highly centralized and vulnearble to technical and non-technical attacks.
Decentralized fault tolerance is one approach to securing these important
services and making networked communication safer.

While the primary purpose of our proposed fault tolerance technique is the
threat of message blocking or corruption, it can provide some improvements
to secrecy and privacy.
For example, if a message is broken into parts and each part is sent along
a different random subset of routes, an attacker who succesfully compromises
one part of the message will still be unable to compromise the rest.

Our present contributions are limited in several ways.
The partial trust model, while making fewer assumptions than web of trust
approaches, still depends on some transitivity of trust,
which may be a questionable assumption in many cases.
Better trust models are still needed.

The primary limitation of our structured network approach is that
link structure is imposed rather than self-organized.
This requirement may be appropriate for appliations such as
wireless sensor networks,
or slow-changing institutional infrastructure,
in which the architect has considerable control over link structure.
But in general, it remains an open question whether self-organized networks
can be restructured, or buit from the ground up in such a way that
structured multipath fault tolerance technqiues can be applied.
Similarly, structured network topologies such as the butterfly are defined
only for specific values.
Although these values can be as large as desired,
how to apply methods such as ours to networks with an intermediate number
of nodes remains an open question.

@@

We have developed a partial trust model which enables a formal analysis
of the effect of decentralized network structure on fault tolerance properties.
We have also proposed a general technique for achieving and evaluating adversarial
fault tolerance in a structured network with partial trust.
We found that the probability of an adversary causing an undetectable error
decreases exponentially as the number of redundant paths between the
neighborhoods of the sender and receiver grows.
This property puts attackers at a disadvantage, creating a stabilizing
asymmetry which disincentivizes attack.
We also presented a specific implementation of the multipath fault tolerance
technique on a wraparound butterfly network topology and proved that the
number of redundant paths grows exponentially with number of network hops
that can be trusted.
Our results are directly applicable to architectures in which the link structure
can be imposed by the architect,
and provide a formalism that can be used more generally to evaluate the role
of network structure and redundancy on the fault tolerance of decentralized
networks.

% Acknowledgments
\begin{acks}
\end{acks}
